\LARGE \bf Attack Graph Generation for Micro-service Architecture

### 2018-08-04 paper_own_docker/main.tex
Some modifications in the text of the main section of the paper.

In this work we model an attack graph as a sequence of atomic attacks. Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege. A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container. For example, let us suppose that an attacker wants to have access to a database of a certain website. In order to reach the database, he has to pass other containers between him and the database. He does that by finding a vulnerability to exploit and give access to the container's neighbors. After a successful exploitation of a chain of intermediate containers, he finally has access to the database and its functions. Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security. For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.

@@

Atomic attacks are fundamental building blocks in our attack graph. A single atomic attack represents a successful vulnerability exploitation. A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph. For an atomic attack to be executed, two constraints are imposed. First, the containers have to be connected between each other, so that physical access can be ensured. Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level. We model the privileges into a hierarchy. The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin). VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been infected. Since VOS are on some hosts, they are in the lower level of hierarchy.

Furthermore, in order for an atomic attack to be performed, a certain precondition has to be met. Preconditions are privilege levels that are required so that a vulnerability can be exploited. When an atomic attack is successfully executed, a postcondition is obtained. Postconditions are privileges acquired as a result of a successful attack. Both the Pre- and Postconditions are transformed from pre- and postcondition rules. We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.

@@

In order to show how the attack graph generation works in practice, we present a small example. The example is taken from the Netflix OSS Github repository. Displayed on figure \ref{TopologyGraph} is the topology of the example. The topology consists of "Outside" node, "Docker daemon" and the a subset of the containers. On figure \ref{AttackGraph}, we can see a part of the resulting attack graph. An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege. Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege. Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege. It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka. Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.

Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig. \ref{AttackGraphSystem}). The Topology Parser reads the underlying topology of the system and converts it into a more machine readable format, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.

@@

Another thing that we take into account is the privileged access. Some containers require certain privileges over the docker daemon in order to function properly. In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file . An attacker with access to these containers, has also access to the docker daemon. And once he has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.

@@

\begin{table*}[t]
	\begin{center}
		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
			\hline
			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\

@@

	\label{table_scalability}
\end{table*}[t]

@@

The algorithm requires the topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
Then into a while loop we iterate through every node, check its neighbors and add the edges. If the neighbor was not passed, then we add it to the queue. The algorithm terminates when the queue is empty. It is characterized by the following properties:

>>>>

In this work we model an attack graph as a sequence of atomic attacks. Each atomic attack represents a transition from a component(with its privilege) to either the same component with a higher privilege or to a neighbor component with a new privilege. A goal of an attacker would be to perform multiple atomic attacks to get to the desired goal container. For example, let us suppose that an attacker wants to have access to a database of a certain website. In order to reach the database, he has to pass other containers between him and the database. He does that by finding a vulnerability to exploit and give access to the container's neighbors. After a successful exploitation of multiple intermediate containers, he finally has access to the database and its functions. Even though attack graphs model the attacker scenario from an attackers perspective, they are of crucial importance in computer security. For example, a system administrator would be interested to have an overview of the attack paths that an attacker could exploit, in order to harden the security of a given enterprise system.

@@

Atomic attacks are fundamental building blocks in our attack graph. A single atomic attack represents a successful vulnerability exploitation. A consecutive sequence of atomic attacks represents a path in an attack graph and multiple attack paths constitute an attack graph. For an atomic attack to be executed, two constraints are imposed. First, the containers have to be connected between each other, so that physical access can be ensured. Second, the attacked container should contain some vulnerability that the attacker can exploit and gain a privilege level. We model the privileges into a hierarchy. The privileges in ascending order are: None, VOS(User), VOS(Admin), OS(User) and OS(Admin). VOS means that the privilege is connected to a virtual machine, while OS means that the host machine has been compromised. Since VOS are hosted on some machines, and their exploitation does not imply exploitation of the host machine, they are in the lower level of hierarchy.

Furthermore, in order for atomic attacks to be performed, certain preconditions have to be met. Preconditions are privilege levels that are required so that a vulnerability can be exploited. When an atomic attack is successfully executed, a postcondition is obtained. Postconditions are privileges acquired as a result of a successful attack. Both the Pre- and Postconditions are transformed from pre- and postcondition rules. We use in our attack graph generator the pre- and postconditions from (reference) which are manually selected by experts and evaluated.

@@

In order to show how the attack graph generation works in practice, we present a small example. The example is taken from the Netflix OSS Github repository. Displayed on figure \ref{TopologyGraph} is the topology of the example. The topology consists of "Outside" node, "Docker daemon" node and the a subset of other nodes. On figure \ref{AttackGraph}, we can see a part of the resulting attack graph. An example path than an attacker to take would be to first attack the Zuul container and gain USER privilege. Then with this USER privilege it can exploit another vulnerability to gain ADMIN privilege. Once the ADMIN privilege has been obtained on Zuul, the attacker can attack the Eureka container and gain ADMIN privilege. It is important to note that this is not the only path that the attacker can take in order to have ADMIN privileges on Eureka. Another path would be to use another Zuul vulnerability to gain directly ADMIN privileges and then attack the Eureka container.

Our attack graph generator is composed of three main components: Topology Parser, Vulnerability Parser and Attack Graph Parser(Fig. \ref{AttackGraphSystem}). The Topology Parser reads the underlying topology of the system and converts it into to a format needed for our Attack Graph Parser, the Vulnerability Parser generates the vulnerabilities for each of the images and the Attack Graph Parser generates the attack graph from the topology and vulnerabilities files.

@@

Another consideration that we take into account is the privileged access. Some containers require certain privileges over the docker daemon in order to function properly. In docker this is usually done either by mounting the docker socket or specifying the keyword "privileged" in the docker-compose.yml file . An attacker with access to these containers, has also access to the docker daemon. Once the attacker has access to the docker daemon, he has potentially access to the whole microservice system, since every container is controlled and hosted by the daemon.

@@

\begin{table*}
	\begin{center}
		\begin{tabular}{ |c|c|c|c|c|c|c|c| } 
			\hline
			Statistics & example\_1 & example\_5 & example\_20 & example\_50 & example\_100 & example\_500 & example\_1000 \\

@@

	\label{table_scalability}
\end{table*}

@@

The algorithm requires a topology and a dictionary of the exploitable vulnerabilities as an input and the output is made up of the nodes and the edges that make the attack graph. 
The algorithm first initializes the nodes, edges, queue and the passed nodes. Afterwards it generates the nodes which are a combination of the image name and the privilege level.
Then into a while loop we iterate through every node, check its neighbors and add the edges if the conditions are satisfied. If the neighbor was not passed, then we add it to the queue. The algorithm terminates when the queue is empty. Furthermore BFS is characterized by the following properties:
